Red-Giant Hot Jupiters: Brilliant Radio Beacons?

### 2015-06-24 ms.tex
minor table update

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}[htdp]
\caption{Detectability of Hot Jupiters with Current and Future Radio Telescopes.}
\begin{center}
\begin{tabular}{c|ccc} \hline \hline\\[-0.5pc]
Instrument & Band & Sensitivity & Time  \\[.25pc]
 &  & $\mu$Jy~hr$^{1/2}$ &  hr \\[0.25pc] 
\hline\\[-0.5pc]
GMRT & 220~MHz &  \\
HERA  & 70~MHz  &  &  \\
LOFAR  & 120~MHz  &  &  \\
LWA  & 70~MHz  &  &  \\
SKA  & 200~MHz  &  &  \\
UTR-2 & & & \\
VLA  & P-band (270-430~MHz)  \\ \hline
\end{tabular}
\end{center}
\label{tab:sens}
\tablecomments{Time estimates to reach 10~$\mu$Jy RMS.  We consider only
telescopes that can reach this in less than XX hours without
being confusion limited.}
\end{table}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}[htdp]
\caption{Detectability of Hot Jupiters with Current and Future Radio Telescopes.}
\begin{center}
\begin{tabular}{c|ccc} \hline \hline\\[-0.5pc]
Instrument & Band & Sensitivity & Time  \\[.25pc]
 &  & $\mu$Jy~hr$^{1/2}$ &  hr \\[0.25pc] 
\hline\\[-0.5pc]
ASKAP & 700-1700~MHz & 37 & 3.4 \\ % table 3 of http://www.atnf.csiro.au/projects/askap/config.html
GMRT & 220~MHz &  \\
HERA  & 70~MHz  &  &  \\
LOFAR  & 120~MHz  &  &  \\
LWA  & 70~MHz  &  &  \\
SKA  & 200~MHz  &  &  \\
UTR-2 & & & \\
VLA  & P-band (270-430~MHz)  \\ \hline
\end{tabular}
\end{center}
\label{tab:sens}
\tablecomments{Time estimates to reach 10~$\mu$Jy RMS.  We consider only
telescopes that can reach this in less than XX hours without
being confusion limited.}
\end{table}
